% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Cheng Chen}

% {E-mail}{mobilephone}{homepage}
% be careful of _ in emaill address
\contactInfo{Graduate Student}{Shanghai}{12/27/1991}
\otherInfo{ch.ch@outlook.com}{(+86) 131-2773-7652}
% {E-mail}{mobilephone}
% keep the last empty braces!
%\contactInfo{xxx@yuanbin.me}{(+86) 131-221-87xxx}{}
 
\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{East China University of Science and Technology (ECUST)}, Shanghai, China}{2014 -- Present}
\textit{Graduate student} in Control Science and Engineering, expected June 2017
\datedsubsection{\textbf{Shandong University of Technology}, Zibo, Shandong}{2010 -- 2014}
\textit{B.S.} in Automation


\section{\faCogs\ Skills}
\begin{itemize}[parsep=1ex]
  \item Familiarity with \emph{Java} \emph{Python} and \emph{C Language}.
  \item Experience on Python Development
  \item Know about \emph{SQL} language, and \emph{MySQL}.
  \item Know about \emph{Git}, able to use some git commands to maintain code.
  \item Know about \emph{Jenkins}, able to use \emph{Jenkins} to build some Jobs.
  \item Able to use \LaTeX   to typeset article and \emph{Markdown} is also used to do some daily records.
  \item Languages: English - Fair (CET-4： 508， CET-6: 484), Mandarin - Native speaker.
\end{itemize}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Micron Inc.} Shanghai, China}{2015.8 -- 2016.4}
\role{Intern}{}
Automation test around tools Development

1. Tool Development

\begin{itemize}
\item Device Management Tool Development
\item The Timeline of Team Members' Jira Tasks Development
\item Weekly Test Summary Report Tool Development
\end{itemize}

2. Building some Jenkins Jobs

3. New Test Platform Test

4. Organizing a team building



% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}



\section{\faHeartO\ Honors and Awards}
\begin{itemize}
\datedline{\item Win school-level scholarship four school years in a row.}{}
\datedline{\item Win Merit students of SDUT.}{2013-2014 schoolyear}
\datedline{\item Win first level graduate student scholarship.}{2014-2015 schoolyear}

\end{itemize}
\section{\faInfo\ Self-evaluation}
\begin{itemize}[parsep=1ex]
  \item Have strong curiosity, and have strong interest in Internet technology.
  \item Be Good at getting information and have strong ability to solve some problems.
  \item Amicable and frank, able to work hard and have good sense of responsibility, have good team-work spirit.
  \item Hospitable to new things; Ability to think and learn independently.
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
